### 2016-03-10 paper/results.tex
yasu

\section{Experimental results} \label{section:results}

>>>>

\section{Experimental results} \label{section:results}
We have implemented the algorithms in C++ and conducted the experiments
on Linux PCs with Intel Core i7 processor with 4 cores, enabling 8 threads
with the hyper threading technology. We have used the Graph-cuts
optimization code written by Veksler, using the libraries provided by
Boykov and Kolmogorov~\cite{middle_bury,2,3,4_below}.
% [2] Fast Approximate Energy Minimization via Graph Cuts.
%         Y. Boykov, O. Veksler, and R. Zabih.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 23, no. 11, pages 1222-1239, November 2001.  
%
%     [3] What Energy Functions can be Minimized via Graph Cuts?
%         V. Kolmogorov and R. Zabih. 
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 2, pages 147-159, February 2004. 
%         An earlier version appeared in European Conference on Computer
%         Vision (ECCV), May 2002.
%
%     [4] An Experimental Comparison of Min-Cut/Max-Flow Algorithms for
%         Energy Minimization in Vision. 
%         Y. Boykov and Vladimir Kolmogorov.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 9, pages 1124-1137, September 2004. 
We have used the QPBO and TRW-S implementations by
Kolmogorov~\cite{msr_link?,trw_link}.

\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/result_layered_depthmap.pdf}
 \caption{}\label{fig:result_layered_depthmap}
\end{figure}
